Matroids from families of null hypotheses

### 2013-08-08 presentation/presentation.tex
some changes on modesim

\begin{frame}
\frametitle{Circuit axioms}

Consider $S$ and a collection of subsets $\mathscr{C}$ for which holds
\begin{enumerate}
\item $C_1 \neq C_2 \in \mathscr{C}$, then $C_1 \nsubseteq C_2$,
\item $C_1 \neq C_2 \in \mathscr{C}$, and $i \in C_1 \cap C_2$ then
   $\exists C_3 \subseteq (C_1 \cup C_2)$,
\end{enumerate}
then $\mathscr{C}$ is the set of circuits of a matroid $M$ on $S$
\begin{itemize}

\begin{frame}
\frametitle{Independence axioms}

\begin{block}
  Consider $S$ and a collection of subsets $\mathscr{I}$ for which
  holds
  \begin{enumerate}{Independence}
  \item $\emptyset \in \mathscr{I}$,
  \item $I \in \mathscr{I}$ and $J \subseteq I$ then $J \in
    \mathscr{I}$,
  \item $I,J \in \mathscr{I}$, $|I| = |J + 1|$ then $\exists j \in I
    \setminus J$ such that $J \cup i \in \mathscr{I}$,
  \end{enumerate}
  then $\mathscr{I}$ is the set of independent sets of a matroid $M$
  on $S$. This defines an independence relation $i \nsim_M I$ iff
  $I\cap i \in \mathscr{I}$. 
\end{block}
\begin{block}{Circuit}
  $C \subset S$ is a circuit iff $C \neq \mathscr{I}$ and for all $I
  \subset C$, $I \in \mathscr{I}$ (\ie minimally dependent set)
\end{block}

>>>>

% \begin{frame}
% \frametitle{Circuit axioms}

% Consider $S$ and a collection of subsets $\mathscr{C}$ for which holds
% \begin{enumerate}
% \item $C_1 \neq C_2 \in \mathscr{C}$, then $C_1 \nsubseteq C_2$,
% \item $C_1 \neq C_2 \in \mathscr{C}$, and $i \in C_1 \cap C_2$ then
%    $\exists C_3 \subseteq (C_1 \cup C_2)$,
% \end{enumerate}
% then $\mathscr{C}$ is the set of circuits of a matroid $M$ on $S$

% \begin{itemize}

% \item \textbf{/Some illustration hereabouts/}

% \end{itemize} % ends low level
% \end{frame}

\begin{frame}
\frametitle{Independence axioms}
\begin{block}{Independence}
  Consider $S$ and a collection of subsets $\mathscr{I}$ for which
  holds
  \begin{enumerate}
  \item $\emptyset \in \mathscr{I}$,
  \item $I \in \mathscr{I}$ and $J \subseteq I$ then $J \in
    \mathscr{I}$,
  \item $I,J \in \mathscr{I}$, $|I| = |J + 1|$ then $\exists j \in I
    \setminus J$ such that $J \cup i \in \mathscr{I}$,
  \end{enumerate}
  then $\mathscr{I}$ is the set of independent sets of a matroid $M$
  on $S$. This defines an independence relation $i \nsim_M I$ iff
  $I\cap i \in \mathscr{I}$. 
\end{block}

\begin{block}{Circuit}
  $C \subset S$ is a circuit iff $C \neq \mathscr{I}$ and for all $I
  \subset C$, $I \in \mathscr{I}$ (\ie minimally dependent set)
\end{block}
\end{frame}
